Blocking-resistant communication\\through domain fronting

### 2014-07-31 docs/meek.tex
Overhead discussion.

The underlying TCP stream is broken into chunks so that
There must therefore be some way of making sure that chunks
are correctly reassembled at the other end,
in order and without gaps and duplicates.
\meek\ takes a naive approach: requests and responses are strictly serialized.
The client doesn't send a second chunk of data
(i.e, make another HTTPS request) until it has
receive the response to the first request.
The underlying stream is simply the concatenation
of chunks in the order they arrive.
Doing it this way is simple and guarantees correctness,
but has performance drawbacks because there is a full round-trip
between every send.
The performance drawbacks are not inherent to the design:
it is domain fronting, not HTTP encoding, that is the fundamental strength of the system.
Section~\ref{sec:futurework} describes more efficient encodings
that enable multiple requests in parallel.

@@

% Overhead estimate.
As discussed in Section~\ref{sec:trafficanalysis},
the same TLS session is used for many requests,
so the overhead of the TLS handshake is amortized.
Tor uses fixed-size cells of 514 bytes~\cite[Section~0.2]{tor-spec}.
% 514 → 543 → 957 → 1079

>>>>

The underlying TCP stream is broken into chunks so that
There must therefore be some way of making sure that chunks
are correctly reassembled at the other end,
in order and without gaps and duplicates.
\meek\ takes a naive approach: requests and responses are strictly serialized.
The client doesn't send a second chunk of data
(i.e, make another HTTPS request) until it has
receive the response to the first request.
The underlying stream is simply the concatenation
of chunks in the order they arrive.
Doing it this way is simple and guarantees correctness,
but has performance drawbacks because there is a full round-trip
between every send.
The performance drawbacks are not inherent to the design:
it is domain fronting, not HTTP encoding, that is the fundamental strength of the system.
Section~\ref{sec:discussion} describes more efficient encodings
that enable multiple requests in parallel.

@@

As an encrypted tunneling protocol, meek adds some overhead.
Each chunk of data gets an HTTP header, and then the HTTP
request is wrapped in a TLS Application Data record.
We estimate the overhead when meek is used to transport Tor.
Tor uses fixed-size cells of 514 bytes~\cite[Section~0.2]{tor-spec}.
Each cell is wrapped in a TLS Application Data record, which adds 29 bytes
using a GCM ciphersuite.
% (in Tor version~0.2.4.22 using a GCM ciphersuite).
This 543-byte record is what is received by \meekclient,
which adds an HTTP header whose length is about 400 bytes
(varying slightly depending on the length of the Host field).
The HTTP request goes into its own TLS Application Data record,
which adds about 50~bytes
(depending on how much padding is used by the ciphersuite selected by the web service).

% 514 → 543 → 956 → 1013

\begin{center}
\begin{tabular}{r@{}r l}
          &    514 & Tor cell \\
          &  $+$29 & Tor TLS record \\
$\approx$ & $+$400 & meek HTTP header \\
$\approx$ &  $+$50 & meek TLS record \\
\hline
$\approx$ &   1000 & total
\end{tabular}
\end{center}

% >>> (1*543+450.)/(1*543)
% 1.828729281767956
% >>> (2*543+450.)/(2*543)
% 1.4143646408839778
% >>> (3*543+450.)/(3*543)
% 1.276243093922652
\noindent
The total overhead varies according to the length
of the Host field and the specifics of the intermediate web service's TLS,
but is somewhere in the neightborhood of $(543+450)/543-1\approx83$\%.
This is the worst case, when Tor sends a single cell.
Tor can bunch multiple cells into one transmission;
if two cells are sent at once, the overhead drops to
${\approx}41$\%; if three, it is ${\approx}28$\%.
Bulk uploads and downloads tend to bunch many cells at once.
Persistent HTTP connections as used by Psiphon reduce overhead further,
because only one HTTP header is sent for a large number of transmissions.
Empty polling requests also use bandwidth,
but they are sent only when the connection is idle
so they don't affect upload or download speed.
As is discussed in Section~\ref{sec:trafficanalysis},
\meekclient\ reuses the same TLS connection for many requests,
so the fixed overhead of the initial TLS handshake is amortized.

There is additional latency overhead caused by the extra network hop:
rather than accessing the Tor bridge directly,
the client first goes through the intermediate web service before
reaching the bridge.
How much latency this adds, of course depends on the network location
of the client, web service, and Tor bridge.
Strict serialization of requests and responses
becomes a problem with large round-trip times,
because bandwidth becomes a function of latency.
Section~\ref{sec:discussion} describes ways to improve
performance with high latencies;
Psiphon's use of persistent connections as described in this section is one of them.
